Model Recognition as Planning

### 2018-05-23 doc/aaai-19/model-recognition.tex
notes added on model recognition

\section{Model Recognition as Planning}
\label{sec:asPlanning}
Now we show a classical planning compilation for computing the {\em observation edit distance} $\delta(\mathcal{M},\mathcal{T})$ for each $\mathcal{M}\in M$. The compilation follows these assumptions
\begin{enumerate}
\item The initial state $s_0\in\mathcal{T}$ is {\em fully observable}.
\item Intermediate actions $a_i\in\mathcal{T}$ and states $s_i\in\mathcal{T}$ s.t. {\small $1\leq i\leq n$}, can be {\em partially observed}. This means that some fluents in $s_i$ may be missing because its value is unknown. In the extreme, entire states $s_i$ can be missing. 
\item $\mathcal{T}$ is {\em noiseless}, meaning that if a fluent or an action is observed it is the correct value. 
\end{enumerate}

@@

>>>>

\section{Model Recognition as Planning}
\label{sec:asPlanning}
Now we show a classical planning compilation for computing the {\em observation edit distance} $\delta(\mathcal{M},\mathcal{T})$ for each $\mathcal{M}\in M$. The compilation follows these assumptions
\begin{enumerate}
\item The initial state $s_0\in\mathcal{T}$ is {\em fully observable}.
\item Intermediate actions $a_i\in\mathcal{T}$ and states $s_i\in\mathcal{T}$ s.t. {\small $1\leq i\leq n$}, can be {\em partially observed}. This means that some fluents in $s_i$ may be missing because its value is unknown. In the extreme, entire states $s_i$, {\small $1\leq i\leq n$}, can be missing. 
\item $\mathcal{T}$ is {\em noiseless}, meaning that if a fluent or an action is observed it is the correct value. 
\end{enumerate}

@@

The {\em \strips\ probability distribution} assigns the same probabaility value to any hypothesis model $\mathcal{M}\in M$ that can reproduce the given observation $\mathcal{T}$. As a rule of thumb, the less information observed the more different models can reproduce observations. If we assume that the observed agent is acting rationally, like in {\em plan recognition as planning}~\cite{ramirez2012plan,ramirez2009plan}, one can define probability distributions that consider as more probable hypothesis the ones that reproduce observations in less steps. This an interesting research direction, specially for the particular case $\mathcal{T}=\tup{s_0, s_n}$ where observations are {\em input-output} examples.
